Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-27 csf2/main.tex
7a

So far, the considered trace models do not let us express speculative execution attacks such as Spectre~\cite{}\MP{cits}. 
For this, we extend the earlier trace model (see \Cref{subsec:scct:tracemodel}) so that the security tags ($\securitytag$) carry additional information about the kind of private data leakage, i.e., the type of speculative leak.
Moreover, we add base-events signalling the beginning of a speculative execution ($\ev{Spec}$), a barrier ($\ev{Barrier}$) that signals that any speculative execution may not go past it, as well as a rollback event ($\ev{Rlb}$), which signals that execution resumes to where speculation started.

@@

We conclude this section by defining the ultimate property of interest for secure compilers: \gls*{specms}.
\begin{definition}[\gls*{specms}]\label{def:trace:specmsdef}
  $
  \specmssafe=\sigma_{\sim_{\mathghost}}\left(\msscctsafe\right)\cap\sssafe
  $
\end{definition}

@@

When modeling some thing using formal methods, the intent is to do so faithfully. 
That is why it is important to ensure that the properties considered in \Cref{sec:casestud:rtp} follow this ideal.
It is relatively straightforward to see that, e.g., $\mssafe$ models a basic memory safety property. 
But, what about $\sigma_{\sim^{\Ltms}_{\Lms}}\left(\mssafe\right)$?
It is not immediately obvious that the resulting property after projecting it from $\Lms$-level to $\Ltms$-level is similar in spirit to the original $\mssafe$ property (\Cref{def:trace:msdef}) and this is what needs to be discussed when using the presented framework.
Let us investigate the involved projections from the case study.

>>>>

So far, the considered trace models do not let us express speculative execution attacks such as Spectre~\cite{kocher2019spectre}. 
For this, we extend the earlier trace model (see \Cref{subsec:scct:tracemodel}) so that the security tags ($\securitytag$) carry additional information about the kind of private data leakage, i.e., the type of speculative leak.
Moreover, we add base-events signalling the beginning of a speculative execution ($\ev{Spec}$), a barrier ($\ev{Barrier}$) that signals that any speculative execution may not go past it, as well as a rollback event ($\ev{Rlb}$), which signals that execution resumes to where speculation started.

@@

We conclude this section by defining the ultimate property of interest for secure compilers: \gls*{specms}.
\begin{definition}[\gls*{specms}]\label{def:trace:specmsdef}
  $
  \specmssafe := \sigma_{\sim_{\mathghost}}\left(\msscctsafe\right)\cap\sssafe
  $
\end{definition}

@@

Compiler designers need to be careful that their implementation preserves the original source language semantics. 
Similar to this, it is important to consider the cross-language relation, which gives a semantic description of the compiler in terms of traces, and check that the original target (resp. source) property is properly translated using the universal (resp. existential) image.
The following discusses this for relations presented in \Cref{sec:casestud:rtp}.
